Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-06-14 manuscript/manuscript.tex
Clean up of figures and graphics
Standardizing figures and graphics, and file names in Images directory.  Ongoing editing and clean up of \captions.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{10-year-trend-monthly.pdf}
  \caption{Monthly SR counts over 10-years}
  \label{fig:10-yr-monthly}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{2-year-trend-monthly.pdf}
  \caption{Monthly SR counts over years 2022-2023}
  \label{fig:2-yr-monthly}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\textwidth]{SRs_by_Agency.pdf}
  	\caption{SR counts by Agency and Cumulative Percentage}
	\label{fig:SRcountbyAgency}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf} 
	\caption{Top 20 SR complaint\_type and Cumulative Percentage} 
	\label{fig:SR_complaints}
\end{figure}

The top 20 complaints contain several of the eight different types of ``Noise'' complaints (Residential, Commercial, Street, Helicopter, etc.). These Noise-related
complaints total 1.435 million in the 2022-2023 dataset, a full 22\% of all complaint types, which, when consolidated, is the most frequently occurring complaint\_type.
Ilegal Parking is second, followed by Heat/Hot Water. Noise complaints are handled by NYPD, as is Illegal Parking and Blocked Driveway complaints, which contributes
significantly to the top ranking of the NYPD as the lead responsible Agency, receiving a full 43\% of all SRs. 
Housing, Preservation, \& Development are 2\textsuperscript{nd}, with 21\%

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width = 0.65\textwidth] {computed_fields.pdf}	
	\caption{Screenshot of data portal showing the ``@computed'' columns}  
	\label{fig:computed-columns}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  	\caption{Number and Percentage of Empty Entries}
	\includegraphics[width=\textwidth]{BlankFields.pdf}
	\label{fig:blank_fields}
\end{figure}

@@

	\begin{figure}[tbp]
	  \centering
	  	\caption{Invalid incident-zip by Agency}
		\includegraphics[width=\textwidth]{invalid_incident_zip.pdf} 
		\label{fig:invalid_incident_zip}
	\end{figure}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{SRs with a Negative Duration by Agency}
	  \includegraphics[width = \textwidth]{negative_duration_SR_barchart.pdf}
	  \label{fig:negative-duration}
\end{figure}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{Negative duration distribution}
	  \includegraphics[width = \textwidth]{negative_duration_SR_violin.pdf}
	  \label{fig:negative-duration-violin}
\end{figure}

@@

	\begin{figure}[tbp]
		\centering
 		\includegraphics[width = \textwidth]{2-year-trend-SR_created_by_top_of_hour.pdf}
		\caption{SRs Created at Top of the Hour}
		\label{fig:tophourcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_created_by_minute_of_busiest_day.pdf}
		\caption{SRs created minute-by-minute on busiest day}
		\label{fig:busiestcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{2-year-trend-SR_closed_by_top_of_hour.pdf}
		\caption{SRs Closed at Top of the Hour}
		\label{fig:tophourclosed}
	\end{figure}

@@

 	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_closed_by_minute_of_busiest_day.pdf}
		\caption{SRs closed minute-by-minute on busiest day}
		\label{fig:busiestclosed}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{post_closed_violin.pdf}
		\caption{Post-Closed resolution\_action\_update\_date \textgreater30 days}
		\label{fig:resolution-violin}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{postClosedBarChart.pdf}
		\caption{Post-Closed resolution\_action\_update\_date \textgreater30 days by Agency}
		\label{fig:resolution-by-agency}
	\end{figure}

@@

\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{non-matchingstreet_nameandlandmark.pdf}
		\caption{Non-matching street\_name \& landmark by Agency}
		\label{fig:landmarkchart}
	\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{10-year-trend-monthly.pdf}
  \caption{10-year (2014-2023) Monthly SR Counts}
  \label{fig:10-yr-monthly}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{2-year-trend-monthly.pdf}
  \caption{Monthly SR Counts for 2022-2023}
  \label{fig:2-yr-monthly}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\textwidth]{SRs_by_Agency.pdf}
  	\caption{SR counts by Agency with Cumulative Percentage}
	\label{fig:SRcountbyAgency}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf} 
	\caption{Top 20 complaint\_type(s) and Cumulative Percentage} 
	\label{fig:SR_complaints}
\end{figure}

The top 20 complaints contain several of the eight different types of ``Noise'' complaints (Residential, Commercial, Street, Helicopter, etc.). These Noise-related
complaints total 1.435 million in the 2022-2023 dataset, a full 22\% of all complaint types, which, when consolidated, is the most frequently occurring complaint\_type.
Illegal Parking is second, followed by Heat/Hot Water. Noise complaints are handled by NYPD, as is Illegal Parking and Blocked Driveway complaints, which contributes
significantly to the top ranking of the NYPD as the lead responsible Agency, receiving a full 43\% of all SRs. 
Housing, Preservation, \& Development are 2\textsuperscript{nd}, with 21\%

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width = \textwidth] {computed_fields.pdf}	
	\caption{Screenshot of Data Portal with ``computed'' Columns}  
	\label{fig:computed-columns}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  	\caption{Number and Percentage of Empty/Blank Entries}
	\includegraphics[width=\textwidth]{BlankFields.pdf}
	\label{fig:blank_fields}
\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\caption{Invalid incident\_zip(s) by Agency}
		\includegraphics[width=\textwidth]{invalid_incident_zip.pdf} 
		\label{fig:invalid_incident_zip}
	\end{figure}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{Negative Duration SRs by Agency}
	  \includegraphics[width = \textwidth]{negative_duration_SR_barchart.pdf}
	  \label{fig:negative-duration}
\end{figure}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{Distribution of Negative Durations}
	  \includegraphics[width = \textwidth]{negative_duration_SR_violin.pdf}
	  \label{fig:negative-duration-violin}
\end{figure}

@@

	\begin{figure}[tbp]
		\centering
 		\includegraphics[width = \textwidth]{2-year-trend-SR_created_by_top_of_hour.pdf}
		\caption{SRs Created at Top-of-the-Hour}
		\label{fig:tophourcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_created_by_minute_of_busiest_day.pdf}
		\caption{SRs Created Minute-by-Minute on Busiest Day}
		\label{fig:busiestcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{2-year-trend-SR_closed_by_top_of_hour.pdf}
		\caption{SRs Closed at Top-of-the-Hour}
		\label{fig:tophourclosed}
	\end{figure}

@@

 	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_closed_by_minute_of_busiest_day.pdf}
		\caption{SRs Closed Minute-by-Minute on Busiest Day}
		\label{fig:busiestclosed}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{post_closed_violin.pdf}
		\caption{Post-Closed resolution\_action\_update\_date(s) \textgreater30 days}
		\label{fig:resolution-violin}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{postClosedBarChart.pdf}
		\caption{Post-Closed resolution\_action\_update\_date(s) \textgreater30 days by Agency}
		\label{fig:resolution-by-agency}
	\end{figure}

@@

\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{non-matchingstreet\_nameandlandmark.pdf}
		\caption{Non-matching street\_name \& landmark by Agency}
		\label{fig:landmarkchart}
	\end{figure}
